|

### 2023-12-04 chapter_2/src/appendix.qmd
init gh-pages branch

# Load fitted models and ppc checks
load(
  file = "../data/temp/models/study_1_fitted.RData"
)
# Load data
list_df <- list()
list_df[["cleaned"]] <- read.csv(
  file = "../data/clean/cleaned_pavlovia.csv"
)
```

@@

### Hypothesis 2

@@

>>>>

# Load fitted models and ppc checks
load(
  file = "../data/temp/models/study_1_fitted.RData"
)
# Load data
list_df <- list()
list_df[["cleaned"]] <- read.csv(
  file = "../data/clean/cleaned_pavlovia.csv"
)
df_study_2 <- read.csv("../data/clean/study_2.csv") |>
  as.data.table()
  #* convert state_district and year variables  to factors
df_study_2 <- df_study_2[
  , year := tstrsplit(year, "-", keep = 1)
][
  , year := as.numeric(year)
][
  , state_district := factor(state_district)
][
  , blue_prop := blue_percent / 100
][
  , red_prop := red_percent / 100
]
```

@@

### $H_2$

@@

#### Summary Statistics of yard sign color measure

```{r}
#| label: tbl-yard-sign-summary
#| tbl-cap: Summary statistics of proportion of colors present on yard signs
names(df_study_2)[names(df_study_2) == 'red_percent'] <- '% Red'
names(df_study_2)[names(df_study_2) == 'blue_percent'] <- '% Blue'
names(df_study_2)[names(df_study_2) == 'white_percent'] <- '% White'

df_study_2_subset <- df_study_2[, c('% Red', '% Blue', '% White')]
datasummary_skim(
  df_study_2_subset
  , notes = "Data source: CAPD Yard Signs."
  , histogram = FALSE
)

```
